Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-15 analysis/Study1.qmd
EGA colours data 10-13

rez_hclust <- make_hclust(data10)
rez_ega <- make_ega(data10, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Itch"]], "F4" = colors[["Breathing"]]))

@@

rez_hclust <- make_hclust(data10f)
rez_ega <- make_ega(data10f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data10f, n = 3, cols = c("F1" = colors[["Breathing"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Hungry"]]))
# rez_cfa10  <- make_cfa(data10f)

@@

rez_hclust <- make_hclust(data11)
rez_ega <- make_ega(data11, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Wind"]], 
                                            "F3" = colors[["Bruise"]], "F4" = colors[["Breathing"]]))

@@

rez_hclust <- make_hclust(data11f)
rez_ega <- make_ega(data11f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data11f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Hungry"]], 
                                            "F3" = colors[["Breathing"]]))
rez_cfa11  <- make_cfa(data11f)

@@

rez_hclust <- make_hclust(data12)
rez_ega <- make_ega(data12, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]]))

@@

rez_hclust <- make_hclust(data12f)
rez_ega <- make_ega(data8af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Pain"]], "F5" = colors[["Sneeze"]]))
# rez_cfa12  <- make_cfa(data12f)

@@

rez_hclust <- make_hclust(data13)
rez_ega <- make_ega(data13, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))

@@

rez_hclust <- make_hclust(data13f)
rez_ega <- make_ega(data13f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))
rez_cfa13  <- make_cfa(data13f)

>>>>

rez_hclust <- make_hclust(data10)
rez_ega <- make_ega(data10, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Bruise"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data10, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Itch"]], "F4" = colors[["Breathing"]]))

@@

rez_hclust <- make_hclust(data10f)
rez_ega <- make_ega(data10f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Wind"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data10f, n = 3, cols = c("F1" = colors[["Breathing"]], "F2" = colors[["Defecate"]], 
                                            "F3" = colors[["Hungry"]]))
# rez_cfa10  <- make_cfa(data10f)

@@

rez_hclust <- make_hclust(data11)
rez_ega <- make_ega(data11, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data11, n = 4, cols = c("F1" = colors[["Hungry"]], "F2" = colors[["Wind"]], 
                                            "F3" = colors[["Bruise"]], "F4" = colors[["Breathing"]]))

@@

rez_hclust <- make_hclust(data11f)
rez_ega <- make_ega(data11f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Wind"]], "C7" = colors[["Pain"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data11f, n = 3, cols = c("F1" = colors[["Wind"]], "F2" = colors[["Hungry"]], 
                                            "F3" = colors[["Breathing"]]))
rez_cfa11  <- make_cfa(data11f)

@@

rez_hclust <- make_hclust(data12)
rez_ega <- make_ega(data12, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Bruise"]], 
  "C5" = colors[["Cough"]], "C6" = colors[["Pain"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12, n = 2, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Bruise"]]))

@@

rez_hclust <- make_hclust(data12f)
rez_ega <- make_ega(data8af, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Wind"]], "C6" = colors[["Bruise"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data12f, n = 5, cols = c("F1" = colors[["Urinate"]], "F2" = colors[["Burp"]], 
                                             "F3" = colors[["Heart"]], "F4" = colors[["Pain"]], "F5" = colors[["Sneeze"]]))
# rez_cfa12  <- make_cfa(data12f)

@@

rez_hclust <- make_hclust(data13)
rez_ega <- make_ega(data13, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Muscles"]], 
  "C5" = colors[["Sex arousal"]], "C6" = colors[["Sneeze"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data13, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))

@@

rez_hclust <- make_hclust(data13f)
rez_ega <- make_ega(data13f, cols = c(
  "C1" = colors[["Heart"]], "C2" = colors[["Hungry"]], "C3" = colors[["Defecate"]], "C4" = colors[["Sneeze"]], 
  "C5" = colors[["Bruise"]], "C6" = colors[["Wind"]], "C7" = colors[["Bruise"]], "C8" = colors[["Blood Sugar"]]))
rez_efa <- make_efa(data13f, n = 4, cols = c("F1" = colors[["Thirsty"]], "F2" = colors[["Heart"]], 
                                            "F3" = colors[["Burp"]], "F4" = colors[["Bruise"]]))
rez_cfa13  <- make_cfa(data13f)
